---
title: "Does height decide income?"
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
---

```{r setup, echo = FALSE}
library(ggplot2)
library(modelr)
library(knitr)
```

## Introduction

It has been claimed that the height of a person is one of the most deciding factors for the persons income. In this short paper we will investigate this assertion by using a dataset from the _National Longitudinal Study_ (U.S. Bureau of Labor Statistics). See `help(heights, package = modelr)`for details.

## Summary statistics

We start by grouping the heights in 8 intervals and report summary statistics.

```{r}
heights$heightInt <- cut(heights$height, breaks = 8)
kable(summary(heights[,1:4]))
kable(summary(heights[,5:9]))
```

## Plots

```{r plot-height-income,  out.width="50%"}
ggplot(heights, mapping = aes(x = height, y = income)) +
  geom_point()
```

```{r}
heightsPosInc <- subset(heights, income > 0)
ggplot(heightsPosInc, mapping = aes(x = heightInt, y = income)) +
  scale_y_continuous(trans = scales::log_trans()) +
  geom_boxplot()
```

```{r}
heightsPosInc <- subset(heights, income > 0)
ggplot(heightsPosInc, mapping = aes(x = height, y = income)) +
  scale_y_continuous(trans = scales::log_trans()) +
  geom_point(position = "jitter") +
  geom_smooth(method = 'lm')
```

```{r}
heightsPosInc <- subset(heights, income > 0)
ggplot(heightsPosInc, mapping = aes(x = height, y = income)) +
  geom_point(position = "jitter") +
  geom_smooth(method = 'lm')
```

## How much do we earn extra per inch

```{r}
summary(lm(income ~ height, data = heights))
```

### Conclusion

One extra inch (2,72 cm) gives you $2982 extra income per year.
**You should have eaten your vegetables**, as your mother told you.
